disaggregation: An \proglang{R} package for Bayesian spatial disaggregation modelling

### 2019-11-21 article.Rnw
Just trying to clarify that the computation is done in cpp but you, the user, work in R.

The \pkg{disaggregation} package is built on Template Model Builder (\pkg{TMB})~\cite{tmb2016}, which is a tool for buidling flexible complex models based on C++. \pkg{TMB} combines the packages CppAD~\cite{bell2012cppad}, for automatic differentiation in C++, Eigen~\cite{guennebaud2010eigen}, a C++ library for linear algebra, and CHOLMOD~\cite{chen2008algorithm}, a package for efficient computation of sparse matrices. The use of these packages allows an efficient implementation of the applied Laplace approximation~\cite{skaug2006automatic} with exact derivatives. \pkg{TMB} calculates first and second order derivatives of the objective function using automatic differentiation~\cite{griewank2008evaluating}.

The \pkg{disaggregation} package contains a C++ function that defines the model and computes the joint likelihood as a function of the parameters and the random effects, in the format expected by \pkg{TMB}. The \pkg{TMB} package then calculates estimates of both parameters and random effects using the Laplace approximation for the likelihood. Evaluation of the objective function and its derivatives is performed in \proglang{R}.

>>>>

The \pkg{disaggregation} package is built on Template Model Builder (\pkg{TMB})~\cite{tmb2016}, which is a tool for buidling flexible complex models based on C++. \pkg{TMB} combines the packages CppAD~\cite{bell2012cppad}, for automatic differentiation in C++, Eigen~\cite{guennebaud2010eigen}, a C++ library for linear algebra, and CHOLMOD~\cite{chen2008algorithm}, a package for efficient computation of sparse matrices. The use of these packages allows an efficient implementation of the automatic Laplace approximation~\cite{skaug2006automatic} with exact derivatives. \pkg{TMB} calculates first and second order derivatives of the objective function using automatic differentiation~\cite{griewank2008evaluating}.

The \pkg{disaggregation} package contains a C++ function that defines the model and computes the joint likelihood as a function of the parameters and the random effects, in the format expected by \pkg{TMB}. The \pkg{TMB} package then calculates estimates of both parameters and random effects using the Laplace approximation for the likelihood. Evaluation of the objective function and its derivatives is performed via \proglang{R}.
